---
title: 'Institutionalized Inequality and Risk Perceptions: Government Intervention
  and Social Welfare during the Novel Coronavirus Pandemic'
output:
  html_document:
    df_print: paged
---

This is a follow up study of 

Breznau, Nate. 2020. “The Welfare State and Risk Perceptions: The Novel Coronavirus Pandemic and Public Concern in 70 Countries.” *European Societies*.

The following files are necessary to run this code

cis2.Rdata                            the data from Breznau (2020)
covid-stringency-index.csv            https://ourworldindata.org/grapher/covid-stringency-index
WID_Data_14082020-111941.xlsx         https://wid.world/data/
ZA6900_v2-0-0.dta                     ISSP RoG 2016
swiid8_3.Rda                          Solt Gini data

Solt, Frederick. 2020. "Measuring Income Inequality Across Countries and Over Time: The Standardized World Income Inequality Database." Social Science Quarterly doi: 10.1111/ssqu.12795



```{r setup}

rm(list = ls(all = T))

wd <- "C:/data" #set your working directory here

wdir <- function(x){
  paste(wd,x, sep = "/")
}


# need pacman package installed to run this
# install.packages("pacman")
pacman::p_load("dplyr","countrycode","car","ggplot2","jtools","sjPlot","sjmisc","sjlabelled","tidyverse","psych","lavaan","kableExtra","ggrepel","stringi","margins","readxl","foreign")

```


```{r load_prep, message = F, warning = F}
# Breznau 2020
load(file = wdir("COVIDiSTRESS/cis2.Rdata"))

# keep only the df of interest
rm(list=ls()[! ls() %in% c("finaldf_C","finaldf_Ca", "wdir", "wd")])

# government response
gov_resp <- read.csv(file = wdir("COVIDiSTRESS/covid-stringency-index.csv"), header = T)

# income concentration
top_inc <- read_xlsx(wdir("COVIDiSTRESS/WID_Data_14082020-111941.xlsx"))

# ISSP RoG
issp16 <- foreign::read.dta(wdir("ZA6900_v2-0-0.dta"), convert.factors = F)

# Solt Gini
load(wdir("COVIDiSTRESS/swiid8_3.Rda"))

# countries to keep
countries <- as.list(finaldf_Ca$cow)

# remove unused countries
issp16$cow <- countrycode(issp16$c_alphan, "iso2c", "cown")

# fix GB
issp16$cow <- ifelse(issp16$c_alphan == "GB-GBN", 200, issp16$cow)
issp16 <- issp16[issp16$cow %in% countries, ]

# NOTE: ISSP has only 32 countries out of the 70 in CiS

```


```{r clean_issp, include = F}
# This code chunk is for study # 3, not used here


# consider using data from the 2006 ISSP to add more countries


# recode all questions so that higher values indicate support for government intervention
issp16 <- issp16 %>%
  mutate(cut_spend = car::recode(v7, '"8"=NA;"9"=NA'),
         spend_jobs = car::recode(v8, '1=5;2=4;3=3;4=2;5=1;else=NA'),
         reg_biz = car::recode(v9, '"8"=NA;"9"=NA'),
         sup_ind = car::recode(v10, '1=5;2=4;3=3;4=2;5=1;else=NA'),
         sup_ind2 = car::recode(v11, '1=5;2=4;3=3;4=2;5=1;else=NA'),
         gov_jobs = car::recode(v21, '1=5;2=4;8=3;3=2;4=1;else=NA'),
         gov_prices = car::recode(v22, '1=5;2=4;8=3;3=2;4=1;else=NA'),
         gov_health = car::recode(v23, '1=5;2=4;8=3;3=2;4=1;else=NA'),
         gov_old = car::recode(v24, '1=5;2=4;8=3;3=2;4=1;else=NA'),
         gov_ind3 = car::recode(v25, '1=5;2=4;8=3;3=2;4=1;else=NA'),
         gov_unemp = car::recode(v26, '1=5;2=4;8=3;3=2;4=1;else=NA'),
         gov_incd = car::recode(v27, '1=5;2=4;8=3;3=2;4=1;else=NA'),
         gov_house = car::recode(v29, '1=5;2=4;8=3;3=2;4=1;else=NA'),
         gov_laws = car::recode(v30, '1=5;2=4;8=3;3=2;4=1;else=NA'),
         gov_surveil = car::recode(v38, '1=5;2=4;8=3;3=2;4=1;else=NA'),
         gov_surveil2 = car::recode(v39, '1=5;2=4;8=3;3=2;4=1;else=NA'),
         gov_open = car::recode(v40, '10=5;9=4.5;8=4;7=3.5;6=3.5;5=3;4=2.5;3=2.5;2=2;1=1.5;0=1;else=NA'),
         gov_secure = car::recode(v41, '1=5;2=4;8=3;3=2;4=1;else=NA'),
         gov_detain = car::recode(v43, '1=5;2=4;8=3;3=2;4=1;else=NA'),
         gov_surveil3 = car::recode(v44, '1=5;2=4;8=3;3=2;4=1;else=NA'),
         gov_surveil4 = car::recode(v45, '1=5;2=4;8=3;3=2;4=1;else=NA'),
         gov_nosay = car::recode(v7, '1=5;2=4;3=3;4=2;5=1;else=NA'),
  )

# create average gov intervention score
issp16df <- select(issp16, cow, cut_spend:gov_nosay)
issp16df$gov_intv <- rowMeans(issp16df[,-1], na.rm=T)

# make a second - inequality related only - scale
issp16df$gov_ineq <- rowMeans(issp16df[,c(3,7,9,12,13)], na.rm =T)

# create an authoritarian scale (just the surveillance items), maybe this is more the type of 'intervention' we want to measure


issp16dfa <- aggregate(issp16df, by = list(issp16df$cow), FUN = mean, na.rm = T)

issp16dfa <- dplyr::select(issp16dfa, cow, gov_intv, gov_ineq)

rm(issp16)

```

```{r clean_blavatnik, warning = F, message = F}

# select measures as of end of March (start of the survey period)

gov_resp <- subset(gov_resp, Date == "24-Mar-20")
gov_resp$cow <- countrycode(gov_resp$Entity, "country.name", "cown")

colnames(gov_resp) <- c("1","2","3","gov_resp","cow")



# select countries
gov_resp <- gov_resp[gov_resp$cow %in% countries, ]

# impute Grenada, Malta and N Macedonia (using Wikipedia info)
# Grenada, strong lockdown, very few cases. Score = 87
# Malta, moderate measures. Score = 70
# N Macedonia, very strong, near total lockdown. Score = 93
gov_resp[72,1] <- 55
gov_resp[72,2] <- 87

gov_resp[73,1] <- 338
gov_resp[73,2] <- 70

gov_resp[74,1] <- 343
gov_resp[74,2] <- 93

gov_resp <- select(gov_resp, cow, gov_resp)

```


```{r clean_ineq, message = F, warning = F}
top_inc <- top_inc %>%
  mutate(cow = countrycode(Country, "country.name", "cown"))

top_inc1 <- subset(top_inc, top_inc$Percentile == "p99p100")
top_inc2 <- subset(top_inc, top_inc$Percentile == "p90p100")
top_inc1 <- subset(top_inc1, !is.na(top_inc1$cow))
top_inc2 <- subset(top_inc2, !is.na(top_inc2$cow))

# Take the mean from 2010-2019 to account for missing data
top_inc1 <- top_inc1[,c(13:22,23)]
top_inc2 <- top_inc2[,c(3:12,23)]
top_inc1$top1 <- rowMeans(top_inc1[,1:10], na.rm = T)
top_inc2$top10 <- rowMeans(top_inc2[,1:10], na.rm = T)
top_inc1 <- select(top_inc1, cow, top1)
top_inc2 <- select(top_inc2, cow, top10)
# china appears multiple times
top_inc1 <- aggregate(top_inc1, by = list(top_inc1$cow), FUN = mean, na.rm = T)
top_inc2 <- aggregate(top_inc2, by = list(top_inc2$cow), FUN = mean, na.rm = T)
rm(top_inc)

```


```{r clean_solt, warning = F, message = F}
rm(swiid)
swiid_summary$cow <- countrycode(swiid_summary$country, "country.name", "cown")

#some countries do not have data since 2016, take most recent available year
swiid_summary <- swiid_summary %>%
  mutate(year = ifelse(country == "Algeria" & year == 2011 | country == "Brunei" & year == 1981 | country == "Bosnia and Herzegovina" & year == 2015 | country == "Grenada" & year == 2008 | country == "Guatemala" & year == 2014 | country == "Iceland" & year == 2015 | country == "India" & year == 2012 | country == "Japan" & year == 2015 | country == "Morocco" & year == 2014 | country == "Pakistan" & year == 2015 | country == "Philippines" & year == 2015 | country == "South Africa" & year == 2015 | country == "United Arab Emirates" & year == 2008, 2016, year))

# trim S. Africa
swiid_summary$gini_disp <- ifelse(swiid_summary$country == "South Africa" & swiid_summary$year == 2016, 55, swiid_summary$gini_disp)


swiid_summary <- subset(swiid_summary, year >= 2016)
swiid_summary <- select(swiid_summary, cow, gini_disp)
swiid_summary <- aggregate(swiid_summary, by = list(swiid_summary$cow), FUN = mean, na.rm = T)
gini_disp <- select(swiid_summary, cow, gini_disp)

rm(swiid_summary)



```

```{r merge_clean}

df <- left_join(finaldf_Ca, gov_resp, by = "cow")
df <- left_join(df, gini_disp, by = "cow")
df <- left_join(df, issp16dfa, by = "cow")
df <- left_join(df, top_inc1, by = "cow")
df <- left_join(df, top_inc2, by = "cow")

# fix Argentina and Indonesia (last top1 observation was 2004)
df$top1 <- ifelse(df$cow == 160, .168, ifelse(df$cow == 850, .085, df$top1))

# take Government Response to pandemic as residuals after predicting what the response should be given the severity of the local outbreak

mR <- lm(gov_resp ~ days_since_peak, conf_delta, data = df)

```


```{r corrs}
cor <- select(df, concern_self, days_since_peak, conf_delta, gov_resp, intervention, gini_disp, top1, socpolicy, gdp)
f1 <- cor(cor, use = "pairwise.complete.obs")


cor1 <- kable(f1, digits = 2, col.names = c("Risk Perception", "Days Since Peak", "New Cases Past Week","Severity of Gov Response", "Timing of Gov Response", "Gini, disposable", "Welfare State", "GDP, per capita"))

kable_styling(cor1)
```




```{r plot1}
ggplot(df, aes(y=gov_resp, x=gov_intv)) +
  geom_point() +
  geom_text(aes(label=iso), vjust = 1.5) +
  geom_smooth(method=lm, se=FALSE) +
  xlab("General Public Preferences for Government Intervention") +
  ylab("Severity of Government Pandemic Measures") +
  theme_classic()
  
```

```{r plot2}
ggplot(df, aes(y=gov_resp, x=gov_ineq)) +
  geom_point() +
  geom_text(aes(label=iso), vjust = 1.5) +
  geom_smooth(method=lm, se=FALSE) +
  xlab("Public Preferences for Government Redistribution") +
  ylab("Severity of Government Pandemic Measures") +
  theme_classic()
  
```
```{r plot3}
ggplot(df, aes(y=gov_resp, x=gini_disp)) +
  geom_point() +
  geom_text(aes(label=iso), vjust = 1.5) +
  geom_smooth(method=lm, se=FALSE) +
  xlab("Gini, post-tax and transfer") +
  ylab("Severity of Government Pandemic Measures") +
  theme_classic()
  
```




```{r plot4}
ggplot(df, aes(y=concern_self, x=gov_resp)) +
  geom_point() +
  geom_text(aes(label=iso), vjust = 1.5) +
  geom_smooth(method=lm, se=FALSE) +
  xlab("Severity of Government Pandemic Measures") +
  ylab("Risk Perceptions") +
  theme_classic()
  
```


```{r adjusted_risk}

# adjust risk for severity of outbreak
m1 <- lm(concern_self ~ days_since_peak + conf_delta + gov_resp, data = df)

# predicted values
df$m1p <- predict.lm(m1, df)

# residuals
df$m1r <- df$concern_self - df$m1p 

# plot fitted v observed
ggplot(df, aes(y=m1p, x=concern_self)) +
  geom_point() +
  geom_text_repel(aes(label=iso), vjust = 1.5) +
  geom_abline(slope=1) +

  xlab("Observed Risk Perceptions") +
  ylab("Predicted Risk Perceptions") +
  theme_classic()

#   geom_smooth(method=lm, se=FALSE) +

mx <- lm(m1r ~ gini_disp, data = df)
summary(mx)
  
```


```{r plot6}


ggplot(df, aes(y=m1r, x=gini_disp)) +
  geom_smooth(method=lm, se=FALSE) +
  geom_text_repel(aes(label=iso), size = 3) +
  xlab("Income Inequality, post-tax and transfer gini") +
  ylab("Risk Perceptions, M1 residuals") +
  theme_classic()

#   
```
```{r plot7}


ggplot(df, aes(y=m1r, x=socpolicy)) +
  geom_smooth(method=lm, se=FALSE) +
  geom_label_repel(aes(label=iso), size = 2.5) +
  xlab("Welfare State, spending and coverage") +
  ylab("Risk Perceptions, M1 residuals") +
  theme_classic()

#   
```

```{r plot8}


ggplot(df, aes(y=m1r, x=gdp)) +
  geom_smooth(method=lm, se=FALSE) +
  geom_label_repel(aes(label=iso), size = 2.5) +
  xlab("GDP, per capita parity") +
  ylab("Risk Perceptions, M1 residuals") +
  theme_classic()

#   
```
```{r plot9}
mid <- 34
# trim gini to get better color display
df$gini_color <- ifelse(df$gini_disp<45, df$gini_disp, 45)

ggplot(data=df, aes(x=conf_delta, y=concern_self, color = gini_color)) +
  geom_point() +
  geom_smooth(method=lm, se=FALSE, color = "gray50", linetype = "dashed") +
  geom_text_repel(aes(label = iso), size = 2.8) +
  scale_color_gradient2(midpoint=mid, low="blue", mid="gray55", high="red", space="Lab") +
  labs(x= "New Case Rate, past week", y = "Coronavirus Concerns", color = "Income Inequality\n(Gini, post\ntax & transfer)") +
      theme(panel.background = element_rect(fill = "white", colour = "grey50"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.title = element_text(size = 10))
```


```{r reg}

# m1x <- lm(concern_self ~ days_since_peak + conf_delta + gov_resp*intervention, data = df)

m2 <- lm(concern_self ~ days_since_peak + conf_delta + gov_resp + gini_disp, data = df)

m3 <- lm(concern_self ~ days_since_peak + conf_delta + gov_resp + socpolicy, data = df)

m4 <- lm(concern_self ~ days_since_peak + conf_delta + gov_resp + gdp, data = df)

m5 <- lm(concern_self ~ days_since_peak + conf_delta + gov_resp + gini_disp + socpolicy + gdp, data = df)

tab_model(m1, m2, m3, m4, m5, p.style = "stars", p.threshold = c(0.10, 0.05, 0.01), show.ci = F, rm.terms = c("(Intercept)"),  dv.labels = c("M1", "M2","M3", "M4","M5","M6"), pred.labels = c("Days Since Curve Inflection", "New Case Rate", "Intervention Severity", "Disposable Income Inequality", "Welfare State Strength", "GDP Per Capita"))
```

```{r std_reg}
tab_model(m1, m2, m3, m4, m5, p.style = "stars", p.threshold = c(0.10, 0.05, 0.01), show.ci = F, rm.terms = c("(Intercept)"), show.std = T, dv.labels = c("M3"), pred.labels = c("Days Since Curve Inflection", "New Case Rate", "Intervention Severity", "Disposable Income Inequality", "Welfare State Strength", "GDP Per Capita"))
```

